---
title: "Socioeconomic Factors on Individuals"
author: "Donna Te, Jiajia Lin, Steven He"
date: "11/14/2022"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(tidyverse)
library(dplyr)
source("../source/AirQualityChart.R")
source("../source/table.R")
source("../source/Summary.R")
source("../source/plot_covid.R")
knitr::opts_chunk$set(echo = TRUE)
```

### Summary
```{r, echo=FALSE}
summary_info
```
In total, there were ```3710``` rows of covid observations. Of these observations, it was found that the greatest number of deaths when observed by race were ```non-hispanic white``` individuals. This was an interesting finding, but could be impacted by numerous factors such as oppression. Oftentimes, people of color may not seek medical attention due to legal or financial reasons, and omissions of these minorities may go unrecorded. We also looked at the race that has the maximum deaths ratio. The result was ```non-hispanic American Indian or Alaska Native```, who are minorities. Because they are minorities, there are many injustices that result in this outcome such as environmental, healthcare, rights, and much more. 

As for the second dataset, the state that has the greatest number of low income non-white population weighted concreation was ```New York```, and this was the same for the high income white population. From these results, we believe that ```New York``` was the outcome for both findings due to the fact that ```New York``` consumes more fossil fuels in its buildings than any other states in the country. To explain the outcome between the two opposite demographics, it may be reliant on the fact that ```New York``` is the fifth-most diverse state but also has one of the greatest income gaps. For these reasons, the combination of diversity in race and income results in ```New York```.


From this aggregated table, we were able to see that Non-Hispanic White individuals had the greatest number of deaths. Although at first glance it was surprising, when observing the proportion of covid deaths, it revealed a significant finding. Because the number of non-white hispanic individuals who were recorded in data was so large, there was also a large number of deaths. Upon looking at the proportions, Non-Hispanic American Indian or Alaska Native and Non-Hispanic Black individuals had the highest proportion of deaths due to covid. 

### Table
```{r}
covid_by_race
```

From this aggregated table, we were able to see that Non-Hispanic White individuals had the greatest number of deaths. Although at first glance it was surprising, when observing the proportion of covid deaths, it revealed a significant finding. Because the number of non-white hispanic individuals who were recorded in data was so large, there was also a large number of deaths. Upon looking at the proportions, Non-Hispanic American Indian or Alaska Native and Non-Hispanic Black individuals had the highest proportion of deaths due to covid. 

### Chart 1
```{r echo=FALSE}
AirGini_plot
```

In order to compare the Gini Coefficient, which measures the income inequality of the state, with the 
Atkinson index, which displays the NO2 concentration. This graph best allows us to visualize how these 
wealth inequalities compare to trends in air pollutants, and whether there is a positive or negative
correlation. We see that there is a high positive correlation between the two factors, meaning that income levels have a strong impact on the level of air pollution. 

### Chart 2
```{r echo=FALSE}
covid_chart
```

This graph shows the correlation between COVID-19 deaths and race. This visualization explains how health of different communities can be harmed by environmental injustice. The data shows that Non-Hispanic American Indians or Alaska Natives have the highest deaths among other communities which suggests the fact of uneven distribution of resources and inequitable exposure to environmental harms.